R Notebook

### 2019-09-04 src/testing_file.Rmd
plot export fixed, now working on hovmoller plot (data restructuring)

@@

p <- levelplot(pstack, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), colorkey=list(space="bottom", at = my.at), par.settings = mapTheme, layout = c(4, 2), names.attr = c("6m", "180m", "370m", "697m", "", "", "", ""))
p + layer(sp.polygons(s, fill = "black")) + layer (sp.polygons(outsidemcp, fill = redtrans, col = NA))

png("../output/maxent/predictions/testplots/rasterVis.png", height = 1024 * 0.707, width = 1024)
p
dev.off()

@@

>>>>

```{r}
library(raster)
library(rgdal)
library(rasterVis)
library(colorspace)

aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/predictions/may", pattern = "^avg_clog.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
brk <- seq(0, 1, 0.1) #for legend
lgc <- sequential_hcl(10, palette = "YlOrRd") #colour scheme from colorspace package
redtrans <- rgb(218, 215, 216, 120, maxColorValue=255) #mcp
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

@@

p <- levelplot(pstack, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), colorkey=list(space="bottom", at = my.at), par.settings = mapTheme, layout = c(4, 2), names.attr = c("6m", "180m", "370m", "697m", "", "", "", ""), margin = FALSE)
p + layer(sp.polygons(s, fill = "black")) + layer (sp.polygons(outsidemcp, fill = redtrans, col = NA))

dev.copy(png, (paste0("../output/maxent/predictions/testplots/rasterVis.png")), width = 1920,height = 1080)
dev.off() # stops automatic saving of the plot to a png))

@@

```{r}
histogram(pstack)
densityplot(pstack)
bwplot(pstack)
```

try hovmoller plotting for depth time

```{r}
#think i need to create a 4d raster with depth and time...
library(ncdf4)

writeRaster(pstack, "../output/maxent/predictions/testplots/pstack.nc", overwrite = TRUE, format = "CDF", varname = "prob", varunit = "p", longname = "dummy netcdf for hovmollers", xname= "X", yname = "Y", zname = "date", zunit = "date")

```{r}
pras6 <- raster::setZ(pras6, as.Date("0000-1-1"), name = "time")
pras180 <- raster::setZ(pras180, as.Date("0000-1-1"), name = "time")
pras370 <- raster::setZ(pras370, as.Date("0000-1-1"), name = "time")
pras697 <- raster::setZ(pras697, as.Date("0000-1-1"), name = "time")
pras1 <- raster::setZ(pras1, as.Date("0000-2-1"), name = "time")
pras2 <- raster::setZ(pras2, as.Date("0000-2-1"), name = "time")
pras3 <- raster::setZ(pras3, as.Date("0000-2-1"), name = "time")
pras4 <- raster::setZ(pras4, as.Date("0000-2-1"), name = "time")
```

```{r}
library(zoo)

old <- setwd(tempdir())
download.file('https://raw.github.com/oscarperpinan/spacetime-vis/master/data/SISmm2008_CMSAF.zip',
'SISmm2008_CMSAF.zip', method='wget')
unzip('SISmm2008_CMSAF.zip')
listFich <- dir(pattern='\\.nc')
stackSIS <- stack(listFich)
stackSIS <- stackSIS*24 ##from irradiance (W/m2) to irradiation Wh/m2

pbrick <- brick(pras6, pras180, pras370, pras697, pras1, pras2, pras3, pras4) #stack the layers

ok new play - try creating an individual netcdf for a month...
```{r}
plst <- list.files("../output/maxent/predictions/testplots/testrasters", full.names = TRUE)

thlst <- list()
anlst <- list()
for (i in 1:length(plst)){
  r <- raster(plst[i])
  aname <- names(r)
  aname <-  str_sub(aname, 13)
  r <- setZ(r, as.numeric(aname), name = "depth")
  thlst[[i]] <- r
  anlst[i] <- aname
}

nstk <- stack(thlst)
nstk <- setZ(nstk, anlst, name = "depth")

writeRaster(nstk, "../output/maxent/predictions/testplots/nstk.nc", overwrite = TRUE, format = "CDF", varname = "prob", varunit = "p", longname = "dummy netcdf for hovmollers", xname= "X", yname = "Y", zname = "depth", zunit = "m")
```
